Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-26 latex/afm-cs-main.tex
Use the same alpha and beta for sim as for experiment.

In addition to imaging static samples, AFM is used to study dynamics
in systems with nanometer-scale features
\cite{Yang:2017im,Shibata:2017da,Shibata:2015jd,Ando:2014ja}. The
image acquisition time of conventional AFMs, however, is typically on
the order of seconds to minutes, severely limiting the time-scales
that can be explored. Driven by the need for faster imaging, there
continue to be many active research efforts to overcome this
challenge. Since an AFM is fundamentally a mechanical microscope, many
of the approaches to high-speed AFM (HS-AFM) have focused on
modifications to the physical components. These have included the use
of small, fast cantilevers \cite{Viani:1999tp,
  braunsmann2010high,Adams:2016hg}, the development of faster
actuators \cite{Maroufi:2015gt,Yong:2012kd,Kenton:2012cm}, and
the application of advanced controllers
\cite{Rana:2018es,Yong:2015gr,butterworth2010adaptive,salapaka2002high}.
By combining different techniques, there are current generation,
high-end instruments that can image at rates on the order of 1-10
frames/sec \cite{Ando:2014ja}. However, the fastest rates are achieved
only over small scan ranges and there remain many systems of interest
whose dynamics are faster even than these instruments can achieve. In
addition, there is a large installed base of much slower AFMs that can
benefit from alternative approaches to improving imaging rate.

@@

\noindent
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[ht!]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV}
    & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    \includesvg[width=0.16\textwidth]{figures/cs20ng_og.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_og_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp_zoom.svg}
    %
    &   \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv_zoom.svg}\\
    % 
    % ------------------------------
    % Row
    % 2
    % --------------------------------------------
    \includesvg[width=0.16\textwidth]{figures/dna_og.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_og_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv_zoom.svg}
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first
    column) Original raster-scanned image. (second column) BPDN
    reconstruction from random, \textcolor{red}{40 pixel long $\mu$-paths with 25\%
    sampling}. (third column) BPVV reconstruction from the same
    sub-sampled data. (remaining columns) Corresponding details from
    the red boxes indicated in the raster image. The results show that
    BPVV reduces the artifacts arising from the horizontal scans of
    the $\mu$-path pattern that appear in BPDN reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\endgroup

@@

A simulation comparison between BPDN and BPVV is shown in
Fig.~\ref{fig:BPTV_demonstration}. The first column shows two raster
scans: the top is a 512 by 512 pixel image of a CS-20NG grating (Ted Pella, USA) acquired
with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of
DNA acquired with an Agilent 5500 AFM. For the CS-20NG grating, we
sampled 15\% of the pixels with 50 pixel $\mu$-paths and 25\%
of the DNA image with 25 pixel long $\mu$-paths. The second columns
shows the full frame reconstructions using BPDN and the third columns
shows the result using BPVV (\textcolor{red}{with $\alpha = ??$ and $\beta = ??$}). The fourth column zooms in on the region
indicated by the red box in column one. Similarly, the fifth and six
columns show the detail of the reconstructions. The reconstruction
results show the artifacts apparent in the BPDN reconstruction are
largely mitigated using BPVV. Thus, in the remainder of the paper, we
focus exclusively on BPVV. These reconstructions wth BPVV took about
1.5 seconds for the DNA image and about 7 seconds for the
CS-20NG (on a typical laptop computer).

>>>>

In addition to imaging static samples, AFM is used to study dynamics
in systems with nanometer-scale features
\cite{Yang:2017im,Shibata:2017da,Shibata:2015jd,Ando:2014ja}. The
image acquisition time of conventional AFMs, however, is typically on
the order of seconds to minutes, severely limiting the time-scales
that can be explored. Driven by the need for faster imaging, there
continue to be many active research efforts to overcome this
challenge. Since an AFM is fundamentally a mechanical microscope, many
of the approaches to high-speed AFM (HS-AFM) have focused on
modifications to the physical components. These have included the use
of small, fast cantilevers \cite{Viani:1999tp,
  braunsmann2010high,Adams:2016hg}, the development of faster
actuators \cite{Maroufi:2015gt,Yong:2012kd,Kenton:2012cm}, and
the application of advanced controllers
\cite{Rana:2018es,Yong:2015gr,butterworth_discrete_2012,salapaka2002high}.
By combining different techniques, there are current generation,
high-end instruments that can image at rates on the order of 1-10
frames/sec \cite{Ando:2014ja}. However, the fastest rates are achieved
only over small scan ranges and there remain many systems of interest
whose dynamics are faster even than these instruments can achieve. In
addition, there is a large installed base of much slower AFMs that can
benefit from alternative approaches to improving imaging rate.

@@

\noindent
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[ht!]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV}
    & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    \includesvg[width=0.16\textwidth]{figures/cs20ng_og.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_og_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp_zoom.svg}
    %
    &   \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv_zoom.svg}\\
    % 
    % ------------------------------
    % Row
    % 2
    % --------------------------------------------
    \includesvg[width=0.16\textwidth]{figures/dna_og.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_og_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv_zoom.svg}
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first
    column) Original raster-scanned image. (second column) BPDN
    reconstruction from random, $\mu$-path sampling.
    (third column) BPVV reconstruction from the same
    sub-sampled data. (remaining columns) Corresponding details from
    the red boxes indicated in the raster image.
    The top row uses 15\% sampling with 50 pixel $\mu$-paths and the
    bottom row uses 25\% sampling with 25 pixel $\mu$-paths.
    The results show that BPVV reduces the artifacts arising from the
    horizontal scans of the $\mu$-path pattern that appear in BPDN
    reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\endgroup

@@

A simulation comparison between BPDN and BPVV is shown in
Fig.~\ref{fig:BPTV_demonstration}. The first column shows two raster
scans: the top is a 512 by 512 pixel image of a CS-20NG grating (Ted Pella, USA) acquired
with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of
DNA acquired with an Agilent 5500 AFM. For the CS-20NG grating, we
sampled 15\% of the pixels with 50 pixel $\mu$-paths and 25\%
of the DNA image with 25 pixel long $\mu$-paths. The second columns
shows the full frame reconstructions using BPDN and the third columns
shows the result using BPVV (with $\alpha = 0.75$ and $\beta = 0.1$). The fourth column zooms in on the region
indicated by the red box in column one. Similarly, the fifth and six
columns show the detail of the reconstructions. The reconstruction
results show the artifacts apparent in the BPDN reconstruction are
largely mitigated using BPVV. Thus, in the remainder of the paper, we
focus exclusively on BPVV. These reconstructions wth BPVV took about
1.5 seconds for the DNA image and about 7 seconds for the
CS-20NG (on a typical laptop computer).
